---
title: "Category Level Current Period Incremental Sales Model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('C:/Users/Fanfan/Desktop/Unilever/data')
library(dplyr)
library(ggplot2)
library(plm)
library(reshape)
library(data.table)
category = read.csv('hc.csv', na.strings = "NULL")

#filter valid retailers
filter_retailer = c("US-XAOC","US-XAOC EX TARGET","KMART REM MKT","US-FOOD","WALMART","AHOLD REM MKT","US-DRUG","PUBLIX XAOC REM MKT","FOOD LION REM MKT","WINN DIXIE REM MKT","WAKEFERN REM MKT","WALMART-WEST","ACME REM MKT","WALMART-SE","WALMART-MID ATLNTC","WALMART-SO CEN","WALMART-NE","WALMART-NO CEN","SHAWS REM MKT","HANNAFORD REM MKT","WEGMANS REM MKT","BILO REM MKT","STOP & SHOP-NY REM MKT","STATER BROS REM MKT","RALEYS REM MKT","HY VEE REM MKT","GIANT-MD REM MKT","STOP & SHOP-NE REM MKT","SHOPPERS REM MKT","GIANT-CAR REM MKT","GIANT EAGLE REM MKT","CUB REM MKT","FARM FRESH REM MKT","ALB_SFWY-CORP")

category = category%>%
  filter(!GEO %in% filter_retailer)

#transformation

##add quadratic terms 
category = category %>%
  mutate(CatbasePrice_sqr = CatbasePrice^2)%>%
  mutate(Catdist_num_sqr = Catdist_num^2)%>%
  mutate(CatPI_TPR_sqr = CatPI_TPR^2)%>%
  mutate(CatPI_Display_sqr = CatPI_Display^2)%>%
  mutate(CatPI_Feature_sqr = CatPI_Feature^2)%>%
  mutate(CatPI_FeatAndDisp_sqr = CatPI_FeatAndDisp^2)%>%
  mutate(CatDiscount_num_sqr = CatDiscount_num^2)%>%
  mutate(CatFeatWODisp_num_sqr = CatFeatWODisp_num^2)%>%
  mutate(CatDispWOFeat_num_sqr = CatDispWOFeat_num^2)%>%
  mutate(CatFeatAndDisp_num_sqr = CatFeatAndDisp_num^2)%>%
  mutate(CatPrice_Display_sqr = CatPrice_Display^2)%>% 
  mutate(CatPrice_Feature_sqr = CatPrice_Feature^2)%>% 
  mutate(CatPrice_FeatAndDisp_sqr = CatPrice_FeatAndDisp^2)%>% 
  mutate(CatPrice_TPR_sqr = CatPrice_TPR^2)


#seperate into two clusters 
retailer_cluster1 = c('BJS', 'CVS', 'DOLLAR GENERAL', 'FAMILY DOLLAR', 'KMART', 'MDC+M', 'RITE AID', 'SAMS', 'TARGET-GM','TARGET-PFRESH', 'TARGET-SUPER', 'WALGREENS', 'WALMART-D1', 'WALMART-SC')

retailer_cluster2 = c('ACME', 'AHOLD', 'ALB-CENSUS', 'BIG Y', 'BILO', 'CUB', 'DEMOULAS', 'FARM FRESH', 'FOOD LION', 'FOOD4LESS','FRED MEYER', 'GIANT-CAR', 'GIANT-MD', 'GIANT EAGLE', 'HANNAFORD', 'HARRIS TEETER', 'HY VEE', 'JEWEL', 'KROGER EX HT','MEIJER', 'PRICE CHOPPER', 'PUBLIX', 'RALEYS', 'SAFEWAY-CENSUS', 'SHAWS', 'SHOPPERS', 'STATER BROS', 'STOP & SHOP-NE','STOP & SHOP-NY', 'WAKEFERN', 'WALMART-NEIGHBOR', 'WEGMANS', 'WEIS', 'WINCO', 'WINN DIXIE')

category_cluster1 = category%>%
  filter(GEO %in% retailer_cluster1)

category_cluster2 = category%>%
  filter(GEO %in% retailer_cluster2)

```


# generate cluster average values
```{r}
cluster1_avg <- aggregate(category_cluster1[, c(3:5,8)], list(category_cluster1$WeekEnding), mean)
#average performance in the cluster 1
ggplot(cluster1_avg, aes(x=Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()+labs(title="cluster1")
ggplot(cluster1_avg, aes(x=Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()+labs(title="cluster1")

ggplot(cluster1_avg, aes(x=CatbasePrice, y = CatbaseDollars)) + geom_point() + geom_smooth()+labs(title="cluster1")
ggplot(cluster1_avg, aes(x=CatbasePrice, y = CatbaseUnits)) + geom_point() + geom_smooth()+labs(title="cluster1")


cluster2_avg <- aggregate(category_cluster2[, c(3:5,8)], list(category_cluster2$WeekEnding), mean)
#average performance in the cluster 2
ggplot(cluster2_avg, aes(x=Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()+labs(title="cluster2")
ggplot(cluster2_avg, aes(x=Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()+labs(title="cluster2")
ggplot(cluster2_avg, aes(x=CatbasePrice, y = CatbaseDollars)) + geom_point() + geom_smooth()+labs(title="cluster2")
ggplot(cluster2_avg, aes(x=CatbasePrice, y = CatbaseUnits)) + geom_point() + geom_smooth()+labs(title="cluster2")
```

#Explorative Analysis

```{r}
summary(category_cluster1)
summary(category_cluster2)
```
##Distribution
**the average number of SKU distributed per store for each retailer below is tend to be possitively correlated with the category base volume of each retailer when the number of distributed SKU is below around 1100. When the number of distributed SKU is above around 1100, further increase SKU number will reduce base volume probabily because consumer might get confuse and lost in so many choices.**
```{r}
#cluster 1 average
ggplot(cluster1_avg, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth() + ggtitle


#cluster 2 average
ggplot(cluster2_avg, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()

#Target
target = filter (category, GEO == 'TARGET')
ggplot(target, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Sams
sam = filter (category, GEO == 'SAMS')
ggplot(sam, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(sam, aes(x = Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()


#Cub
cub = filter (category, GEO == 'CUB')
ggplot(cub, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#CVS
cvs = filter (category, GEO == 'CVS')
ggplot(cvs, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(cvs, aes(x = Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Food LION
food_lion = filter (category, GEO == 'FOOD LION')
ggplot(food_lion, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(food_lion, aes(x = Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Walgreen
walgreens = filter (category, GEO == 'WALGREENS')
ggplot(walgreens, aes(x = Catdist_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(walgreens, aes(x = Catdist_num, y = CatbaseDollars)) + geom_point() + geom_smooth()


```

##Shelf Price
**Price has a curlinear relationship with unit or dollar sales**
**Cub has lower price elasticity than Walmart. Then when incresing price, it's dollar sales even remain stable. Meanwhile, cub has lower average price, and when price is even lower, increasing price can increase unit sales.**
**The pricing elasitisity of Walmart allow it to increase dollar sales by increasing price at a particular price level**

```{r}
#Target
ggplot(target, aes(x = CatbasePrice, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatbasePrice, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Cub
ggplot(cub, aes(x = CatbasePrice, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatbasePrice, y = CatbaseDollars)) + geom_point() + geom_smooth()
```


##Promotion
###number of products on TPR
**For target, there seems to be an optimal number of TPR that can generate the biggest dollar sales.**
**For cub, the sales remain rather stable when changing the number of TPR. non-destination-category retailers like cub might over promoted haircare.**
```{r}
#Target
ggplot(target, aes(x = CatDiscount_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatDiscount_num, y = CatDollars)) + geom_point() + geom_smooth()

#Cub
ggplot(cub, aes(x = CatDiscount_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatDiscount_num, y = CatDollars)) + geom_point() + geom_smooth()
```

###number of products on Display
**For target, the number of display is not clearly positively correlated with category total sales, however it is highly correlated with base sales.Display might have good impact to brand equity and long term sales**
```{r}
#Target
ggplot(target, aes(x = CatDispWOFeat_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatDispWOFeat_num, y = CatDollars)) + geom_point() + geom_smooth()

ggplot(target, aes(x = CatDispWOFeat_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatDispWOFeat_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Cub
ggplot(cub, aes(x = CatDispWOFeat_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatDispWOFeat_num, y = CatDollars)) + geom_point() + geom_smooth()
```

###number of products on Feature
**cub's sale is still not sensitive to the number of features**
**feature didn't show postivie correlation with base sales in target**
```{r}
#Target
ggplot(target, aes(x = CatFeatWODisp_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatFeatWODisp_num, y = CatDollars)) + geom_point() + geom_smooth()

ggplot(target, aes(x = CatFeatWODisp_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatFeatWODisp_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Cub
ggplot(cub, aes(x = CatFeatWODisp_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatFeatWODisp_num, y = CatDollars)) + geom_point() + geom_smooth()

```

###number of products on Feature and Display
**feature and display show postivie correlation with base sales in target**
```{r}
#Target
ggplot(target, aes(x = CatFeatAndDisp_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatFeatAndDisp_num, y = CatDollars)) + geom_point() + geom_smooth()

ggplot(target, aes(x = CatFeatAndDisp_num, y = CatbaseUnits)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatFeatAndDisp_num, y = CatbaseDollars)) + geom_point() + geom_smooth()

#Cub
ggplot(cub, aes(x = CatFeatAndDisp_num, y = CatUnits)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = log(CatFeatAndDisp_num), y = CatDollars)) + geom_point() + geom_smooth()

```

### Discount level of TPR
**target: lower discount may increase category sales for TPR**
**cub: not sensitive**
```{r}
#target
ggplot(target, aes(x = CatPI_TPR, y = CatDollars, color = CatPrice_TPR)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPI_TPR, y = CatUnits, color = CatPrice_TPR)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPI_TPR, y = CatDollars, color = CatPrice_TPR)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPI_TPR, y = CatUnits, color = CatPrice_TPR)) + geom_point() + geom_smooth()
```

### Discount level of Display
**deeper level of discount doesn't show clear increase in unit sales but will hurt dollar sales**
**cub: not sensitive**b
```{r}
#target
ggplot(target, aes(x = CatPI_Display, y = CatDollars, color = CatPrice_Display)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPI_Display, y = CatUnits, color = CatPrice_Display)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPI_Display, y = CatDollars, color = CatPrice_Display)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPI_Display, y = CatUnits, color = CatPrice_Display)) + geom_point() + geom_smooth()
```

### Discount level of Feature
**unit sales is not sensitive, dollar sales decrease when discount is lower.**
```{r}
#target
ggplot(target, aes(x = CatPI_Feature, y = CatDollars, color = CatPrice_Feature)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPI_Feature, y = CatUnits, color = CatPrice_Feature)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPI_Feature, y = CatDollars, color = CatPrice_Feature)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPI_Feature, y = CatUnits, color = CatPrice_Feature)) + geom_point() + geom_smooth()
```
### Discount level of Feature and Display
**unit sales is not sensitive(even negative), dollar sales decrease when discount is lower.**
```{r}
#target
ggplot(target, aes(x = CatPI_FeatAndDisp, y = CatDollars, color = CatPrice_FeatAndDisp)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPI_FeatAndDisp, y = CatUnits, color = CatPrice_FeatAndDisp)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPI_FeatAndDisp, y = CatDollars, color = CatPrice_FeatAndDisp)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPI_FeatAndDisp, y = CatUnits, color = CatPrice_FeatAndDisp)) + geom_point() + geom_smooth()
```

### price of TPR
**lower price, higher unit sales, but dollar sales may be smaller**
```{r}
#target
ggplot(target, aes(x = CatPrice_TPR, y = CatDollars)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPrice_TPR, y = CatUnits)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPrice_TPR, y = CatDollars)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPrice_TPR, y = CatUnits)) + geom_point() + geom_smooth()
```

### price of Display
**cub is not sensitive**
```{r}
#target
ggplot(target, aes(x = CatPrice_Display, y = CatDollars)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPrice_Display, y = CatUnits)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPrice_Display, y = CatDollars)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPrice_Display, y = CatUnits)) + geom_point() + geom_smooth()
```


### price of Feature
**cub is not sensitive**
```{r}
#target
ggplot(target, aes(x = CatPrice_Feature, y = CatDollars)) + geom_point() + geom_smooth()
ggplot(target, aes(x = CatPrice_Feature, y = CatUnits)) + geom_point() + geom_smooth()

#cub
ggplot(cub, aes(x = CatPrice_Feature, y = CatDollars)) + geom_point() + geom_smooth()
ggplot(cub, aes(x = CatPrice_Feature, y = CatUnits)) + geom_point() + geom_smooth()
```


#Modeling
##Distribution and Shelf Price
###Cluster 1
```{r}
attach(category_cluster1)
##check correlation
cor(Catdist_num, CatbasePrice)

##two way fix effect model 
Dollarsfix = plm(log(CatbaseDollars) ~ Catdist_num + Catdist_num_sqr + log(CatbasePrice), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatbaseUnits) ~ Catdist_num + Catdist_num_sqr + log(CatbasePrice), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in Catdist_num, the %increase in CatbaseDollars when Catdis_num is at the cluster average level
exp(Dollarsfix$coefficients[1] + 2 * Dollarsfix$coefficients[2]* mean(category_cluster1$Catdist_num)) - 1

###1% increase in baseprice,  % increase in category base dollar sales
Dollarsfix$coefficients[3]

###1 unit further increase in Catdist_num, the %increase in CatbaseUnits when Catdis_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster2$Catdist_num)) -1 

###1% increase in baseprice,  % increase in category base Units sales
Unitsfix$coefficients[3]

```

###Cluster 2
```{r}
attach(category_cluster2)
##check correlation
cor(Catdist_num, CatbasePrice)

##two way fix effect model 
Dollarsfix = plm(log(CatbaseDollars) ~ Catdist_num + Catdist_num_sqr + log(CatbasePrice), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatbaseUnits) ~ Catdist_num + Catdist_num_sqr + log(CatbasePrice), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)


###1 unit further increase in Catdist_num, the %increase in CatbaseDollars when Catdis_num is at the cluster average level
exp(Dollarsfix$coefficients[1] + 2 * Dollarsfix$coefficients[2]* mean(category_cluster1$Catdist_num)) - 1

###1% increase in baseprice,  % increase in category base dollar sales
Dollarsfix$coefficients[3]

###1 unit further increase in Catdist_num, the %increase in CatbaseUnits when Catdis_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster2$Catdist_num)) -1 

###1% increase in baseprice,  % increase in category base Units sales
Unitsfix$coefficients[3]

```


##Promotion
```{r}
##check correlation
cor(cbind(CatDiscount_num, CatDispWOFeat_num, CatFeatWODisp_num, CatFeatAndDisp_num, CatPI_TPR, CatPI_Display, CatPI_Feature, CatPI_FeatAndDisp, CatPrice_TPR, CatPrice_Display, CatPrice_Feature, CatPrice_FeatAndDisp, CatbaseDollars,CatbaseUnits), use = "pairwise")
```

###TPR
####TPR Cluster 1
```{r}
##two way fix effect model 
####TPR
Dollarsfix = plm(log(CatDollars) ~ CatDiscount_num + CatDiscount_num_sqr + CatPI_TPR + CatPI_TPR_sqr + log(CatPrice_TPR), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatDiscount_num + CatDiscount_num_sqr + CatPI_TPR + CatPI_TPR_sqr + log(CatPrice_TPR), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in CatDispWOFeat_num, the % increase in CatbaseDollars when CatDiscount_num is at the cluster average level
exp(Dollarsfix$coefficients[1] + 2 * Dollarsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatDispWOFeat_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_Disp, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_Disp, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_Disp,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_Disp,  % increase in category base unit sales
Unitsfix$coefficients[5]
```

####TPR Cluster 2
```{r}
##two way fix effect model 
####TPR
Dollarsfix = plm(log(CatDollars) ~ CatDiscount_num + CatDiscount_num_sqr + CatPI_TPR + CatPI_TPR_sqr + log(CatPrice_TPR), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatDiscount_num + CatDiscount_num_sqr + CatPI_TPR + CatPI_TPR_sqr + log(CatPrice_TPR), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in CatDiscount_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_TPR,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_TPR,  % increase in category base unit sales
Unitsfix$coefficients[5]]
```

###Display
####Display Cluster 1
```{r}
####Display
Dollarsfix = plm(log(CatDollars) ~ CatDispWOFeat_num + CatDispWOFeat_num_sqr + CatPI_Display + CatPI_Display_sqr + log(CatPrice_Display), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatDispWOFeat_num + CatDispWOFeat_num_sqr + CatPI_Display + CatPI_Display_sqr + log(CatPrice_Display), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in CatDiscount_num, the units increase in CatbaseDollars when CatDiscount_num is at the cluster average level
exp(Dollarsfix$coefficients[1] + 2 * Dollarsfix$coefficients[2]* mean(category_cluster1$CatDispWOFeat_num))

###1 unit further increase in CatDiscount_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_TPR,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_TPR,  % increase in category base unit sales
Unitsfix$coefficients[5]
```

####Display Cluster 2
```{r}
####Display
Dollarsfix = plm(log(CatDollars) ~ CatDispWOFeat_num + CatDispWOFeat_num_sqr + CatPI_Display + CatPI_Display_sqr + log(CatPrice_Display), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatDispWOFeat_num + CatDispWOFeat_num_sqr + CatPI_Display + CatPI_Display_sqr + log(CatPrice_Display), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in CatDiscount_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_TPR,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_TPR,  % increase in category base unit sales
Unitsfix$coefficients[5]
```


###Feature 
####Feature Cluster 1
```{r}
Dollarsfix = plm(log(CatDollars) ~ CatFeatWODisp_num + CatFeatWODisp_num_sqr + CatPI_Feature + CatPI_Feature_sqr + log(CatPrice_Feature), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatFeatWODisp_num + CatFeatWODisp_num_sqr + CatPI_Feature + CatPI_Feature_sqr + log(CatPrice_Feature), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)


###1 unit further increase in CatDiscount_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_TPR,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_TPR,  % increase in category base unit sales
Unitsfix$coefficients[5]
```

####Feature Cluster 2
```{r}
Dollarsfix = plm(log(CatDollars) ~ CatFeatWODisp_num + CatFeatWODisp_num_sqr + CatPI_Feature + CatPI_Feature_sqr + log(CatPrice_Feature), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatFeatWODisp_num + CatFeatWODisp_num_sqr + CatPI_Feature + CatPI_Feature_sqr + log(CatPrice_Feature), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)


###1 unit further increase in CatDiscount_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_TPR,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_TPR,  % increase in category base unit sales
Unitsfix$coefficients[5]
```

###Display and Feature 

####Display and Feature Cluster 1
```{r}
Dollarsfix = plm(log(CatDollars) ~ CatFeatAndDisp_num + CatFeatAndDisp_num_sqr + CatPI_FeatAndDisp + CatPI_FeatAndDisp_sqr + log(CatPrice_FeatAndDisp), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatFeatAndDisp_num + CatFeatAndDisp_num_sqr + CatPI_FeatAndDisp + CatPI_FeatAndDisp_sqr + log(CatPrice_FeatAndDisp), data = category_cluster1, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in CatDiscount_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_TPR, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_TPR,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_TPR,  % increase in category base unit sales
Unitsfix$coefficients[5]
```

####Display and Feature Cluster 2
```{r}
Dollarsfix = plm(log(CatDollars) ~ CatFeatAndDisp_num + CatFeatAndDisp_num_sqr + CatPI_FeatAndDisp + CatPI_FeatAndDisp_sqr + log(CatPrice_FeatAndDisp), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Dollarsfix)

Unitsfix = plm(log(CatUnits) ~ CatFeatAndDisp_num + CatFeatAndDisp_num_sqr + CatPI_FeatAndDisp + CatPI_FeatAndDisp_sqr + log(CatPrice_FeatAndDisp), data = category_cluster2, index = c("GEO", "WeekEnding"), effect = "twoway", model = "within")
summary(Unitsfix)

###1 unit further increase in CatFeatAndDisp_num, the % increase in CatbaseUnits when CatDiscount_num is at the cluster average level
exp(Unitsfix$coefficients[1] + 2 * Unitsfix$coefficients[2]* mean(category_cluster1$CatDiscount_num)) -1

###1 unit further increase in CatPI_FeatAndDisp, the %increase in CatbaseDollars when CatPI_TPR is at the cluster average level
exp(Dollarsfix$coefficients[3] + 2 * Dollarsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR)) - 1

###1 unit further increase in CatPI_FeatAndDisp, the %increase in CatbaseUnits when CatPI_TPR is at the cluster average level
exp(Unitsfix$coefficients[3] + 2 * Unitsfix$coefficients[4]* mean(category_cluster1$CatPI_TPR, na.rm = TRUE)) - 1

###1% increase in CatPrice_FeatAndDisp,  % increase in category base dollar sales
Dollarsfix$coefficients[5]

###1% increase in CatPrice_FeatAndDisp,  % increase in category base unit sales
Unitsfix$coefficients[5]
```


