---
title: "Tracking Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
    theme: readable
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(zoo)
library(plotly)
library(reshape2)
```

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
#setwd("E:/Data Science Study/User behavior")
daily_funnel <- read.csv("funnel_report.csv")
cohort_activation <- read.csv("cohort_analysis_active.csv")
cohort_conversion <- read.csv("cohort_analysis_conversion.csv")


# data preparation

## daily_funnel data set
###convert date format
daily_funnel <- daily_funnel%>%
  mutate(the_date = as.Date(the_date, "%m/%d/%Y"))
### transform the data to long format for visualization
daily_funnel_melted <- melt(daily_funnel, id.vars = "the_date")
colnames(daily_funnel_melted)[2] = "Groups"

## cohort_activation data set
### calculate months since acquisition for each cohort 
cohort_activation <- cohort_activation %>% 
  mutate(month_lapsed = round((as.yearmon(year_month, "%Y-%m") - as.yearmon(cohort, "%Y-%m"))*12,0),
         cohort = as.yearmon(cohort, "%Y-%m"),
         active_pct = active_pct * 100)%>%
  arrange(cohort, month_lapsed)%>%
  mutate(cohort = factor(cohort))%>%
  filter(cohort != "-" & year_month != "-")

## cohort_conversion data set
### calculate months since acquisition for each cohort 
cohort_conversion <- cohort_conversion %>% 
  mutate(month_lapsed = round((as.yearmon(year_month, "%Y-%m") - as.yearmon(cohort, "%Y-%m"))*12,0),
         cohort = as.yearmon(cohort, "%Y-%m"),
         conversion_rate = conversion_rate * 100,
         retention_rate = retention_rate * 100)%>%
  arrange(cohort, month_lapsed)%>%
  mutate(cohort = factor(cohort))%>%
  filter(cohort != "-" & year_month != "-")
```


User Activity 
=====================================  

Column {.sidebar}
-----------------------------------------------------------------------

Track user activities throughout the time to understand the composition web traffic and how it changes over time.

* New: active today, no event record in history
* Persistent: active in today and yesterday
* Returned: active today, inactive yesterday
* Churned: inactive today, active yesterday
  
```{r}
#input date range

dateRangeInput("dates",
               "Select the date range:",
                start = "2014-01-03",
                end = "2015-03-31",
                min = "2014-01-03",
                max = "2015-03-31",
                format="yyyy/mm/dd")

```

Row 
-----------------------------------------------------------------------

### Avg Daily New Users

```{r}
#output mean value for selected dates

renderValueBox(
  valueBox(value = as.integer(mean(subset(daily_funnel, 
                                          the_date > input$dates[1] & the_date < input$dates[2])$New)), 
           color = "#88a618"))
```

### Avg Daily Persistent Users
```{r}
#output mean value for selected dates

renderValueBox(
  valueBox(value = as.integer(mean(subset(daily_funnel, 
                                          the_date>input$dates[1] & the_date<input$dates[2])$Persistent)), 
           color = "#F29F05"))
```

### Avg Daily Returned Users
```{r}
#output mean value for selected dates

renderValueBox(
  valueBox(value = as.integer(mean(subset(daily_funnel, 
                                          the_date > input$dates[1] & the_date < input$dates[2])$Returned)), 
           color = "#438694"))
```


### Avg Daily Churned Users
```{r}
renderValueBox(
  valueBox(value = as.integer(mean(subset(daily_funnel, 
                                          the_date > input$dates[1] & the_date < input$dates[2])$Churned)), 
           color = "#D92525"))
```


Row 
-----------------------------------------------------------------------

### Trend
```{r}
#filter input dates
#seperate number of churned users as it's negative impact
#display number of churned users as negative values

renderPlot(
  ggplot() + 
    geom_area(data = subset(daily_funnel_melted, 
                            the_date > input$dates[1] & the_date < input$dates [2] & Groups != "Churned"),
              aes(x = the_date, y = value, fill = Groups)) +
    geom_area(data = subset(daily_funnel_melted, 
                            the_date > input$dates[1] & the_date < input$dates [2] & Groups == "Churned")
                     %>% mutate(value = -value), 
              aes(x = the_date, y = value, fill = Groups)) +
    scale_fill_manual(values=c("#D92525", "#F29F05", "#88a618","#438694")) +
    theme(panel.background = element_blank()) +
    ylab("Total Number of Users")
)
```



Cohort Analysis
=====================================  
Column {.sidebar}
-----------------------------------------------------------------------

Divide users into cohorts based on their time of acquisition.
Analyze customer funnel metrics of different cohorts at each month since acquisition to compare cohorts and track status of each cohort. 


```{r}
radioButtons("chart_type", label = "Select chart type:", 
             choices = c("heat map", "line chart"), selected = "heat map")

conditionalPanel(condition = "input.chart_type == 'line chart'",
  selectInput("cohorts_selected", label = "Select cohorts:",
              selected = c("Jan 2014", "Feb 2014","Mar 2014"),
              multiple = TRUE,
              choices = cohort_activation$cohort)
  )
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Activation

```{r}
renderPlot(
  if (input$chart_type == "line chart") {
    ggplot(subset(cohort_activation, cohort %in% input$cohorts_selected), 
           aes(x = month_lapsed, y = active_pct, color = cohort)) + geom_line() + 
      geom_point() + theme(panel.background = element_blank()) +
      ggtitle("Percent Active (%)") +
      xlab("Month since acquisition") +
      ylab("Percent Active (%)")
    }
  else if (input$chart_type == "heat map") {
    ggplot(cohort_activation, aes(month_lapsed, cohort)) + 
      geom_tile(aes(fill = active_pct), colour = "white") + 
      geom_text(aes(label = active_pct)) +
      scale_fill_gradient(low = "#D92525",high = "#88a618") + 
      theme(panel.background = element_blank()) +
      ggtitle("Percent Active (%)") +
      xlab("Month since acquisition")
  })
```

### Conversion

```{r}
renderPlot(
  if (input$chart_type == "line chart") {
    ggplot(subset(cohort_conversion, cohort %in% input$cohorts_selected), 
           aes(x = month_lapsed, y = conversion_rate, color = cohort)) + 
      geom_line() + geom_point() + theme(panel.background = element_blank()) +
      ggtitle("Conversion Rate (%)") +
      xlab("Month since acquisition") +
      ylab("Conversion rate (%)")
    }
  else if (input$chart_type == "heat map") {
    ggplot(cohort_conversion, aes(month_lapsed, cohort)) + 
        geom_tile(aes(fill = conversion_rate), colour = "white") + 
        geom_text(aes(label = conversion_rate)) +
        scale_fill_gradient(low = "#D92525",high = "#88a618") + 
        theme(panel.background = element_blank()) + 
        ggtitle("Conversion Rate (%)") +
        xlab("Month since acquisition")} 
    )
```


### Repeat Purchase

```{r}
renderPlot(
    if (input$chart_type == "line chart") {
      ggplot(subset(cohort_conversion, cohort %in% input$cohorts_selected), 
             aes(x = month_lapsed, y = retention_rate, color = cohort)) + 
        geom_line() + geom_point() + 
        theme(panel.background = element_blank()) + 
        ggtitle("Repeat Purchase Rate (%)") +
        xlab("Month since acquisition") +
        ylab("Repeat Purchase Rate (%)")
      }
    else if (input$chart_type == "heat map") {
      ggplot(cohort_conversion, aes(month_lapsed, cohort)) + 
        geom_tile(aes(fill = retention_rate), colour = "white") + 
        geom_text(aes(label = retention_rate)) +
        scale_fill_gradient(low = "#D92525",high = "green2") +
        theme(panel.background = element_blank()) +
        ggtitle("Repeat Purchase Rate (%)") +
        xlab("Month since acquisition")
      } 
      )
```



